---
title: "cm017-notes_and_exercises.Rmd"
output: github_document
---

Here we explore some lists obtained from the [GitHub API](https://developer.github.com/v3/). 

Load the packages.

```{r message = FALSE}
library(repurrrsive)
library(listviewer)
library(jsonlite)
library(dplyr)
library(tibble)
library(purrr)
```

### Get several GitHub users

`gh_users` is *a recursive list*:

  * one component for each of the 6 GitHub users
  * each component is, in turn, a list with info on the user

```{r}
str(gh_users, max.level = 1)
str(gh_users[[1]], list.len = 6)
```

You can also use `listviewer::jsonedit()` to explore it interactively:

```{r echo = FALSE}
jsonedit(gh_users, mode = "view", elementId = "gh_users")
```


### Name and position shortcuts

Basic usage of `purrr::map()`:

```{r eval = FALSE}
map(gh_users,"login")
gh_users%>%
  map(18)
```


### Extract multiple values

Get user's name and GitHub username for a single user:

```{r}
gh_users[[3]][c("name", "login", "id", "location")]
```

The function `.f` will be `[`. And we finally get to use `...`! 

```{r}
x <- map(gh_users, `[`, c("login", "name", "id", "location"))
x[[1]]$location
```

Some people find this ugly and might prefer the `extract()` function from magrittr.

```{r}
x <- map(gh_users, magrittr::extract, c("login", "name", "id", "location"))
str(x[3:4])
```


### Data frame output

`map_df()`

```{r}
map_df(gh_users, `[`, c("login", "name", "id", "location"))
```

We can also explicitly specify type and build your data frame the usual way.

```{r}
gh_users %>% {
  tibble(
       login = map_chr(., "login"),
        name = map_chr(., "name"),
          id = map_int(., "id"),
    location = map_chr(., "location")
  )
}
```


### Repositories for each user

Meet `gh_repos`. It is a list with:

  * one component for each of our 6 GitHub users
  * each component is another list of that user's repositories (or just the first 30, if user has more than 30)
  * several of those list components are, again, a list

```{r}
str(gh_repos, max.level = 1)
```

Explore it interactively:

```{r echo = FALSE}
jsonedit(gh_repos, mode = "view", elementId = "gh_repos")
```

### Warm up & refresh challenge
Extrat information from lists: full name of first repo

```{r}
gh_repos%>%
  map_
```


