---
title: "cm010 Notes and Exercises: Table Joins"
date: '2017-10-05'
output: github_document
---

```{r}
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(tidyverse))
```


The different join functions that are available.
```{r}
left_join()
full_join()
inner_join()
semi_join()
anti_join()
```

Install the singer library from github directly.
```{r}
install.packages("devtools")
library(devtools)
install_github("joeyBernhardt/singer")
```

Load the singer library.
```{r}
library(singer)
```

Check the songs and locations dataset.
```{r}
View(songs)
View(locations)
glimpse(songs)
glimpse(locations)
```

#Release and Year 

Produce a dataframe with all the albums('release'), the artists('artist_name') and the year('year') in which that album was published.

```{r}
relartyear<-inner_join(locations,songs,by=c("title","artist_name"))%>%
  select(release,artist_name,year)
relartyear
```

Challenge 1
Get the number of releases per year

```{r}
inner_join(locations,songs,by=c("title","artist_name"))%>%
  select(release,artist_name,year)%>%
  group_by(year)%>%
  summarize(number_of_releases=length(release))

inner_join(songs,locations,by="title")%>%
  count(year)
```

#RESHAPING

```{r}
data("singer_locations")
glimpse(singer_locations)
```

**WIDE** dataframe
**LONG** dataframe

```{r}
View(singer_locations)
```

year,artist_hotttnesss, artist_familiarity,duration
```{r}
hfd_y <- singer_locations%>%
                  select(year,artist_hotttnesss, artist_familiarity,duration)
hfd_y%>%
  filter(year>1900)%>%
  ggplot(aes(x = year,y = duration))+
  geom_point()
```

package 'tidyr', 'gather()' : from wide to long

```{r}
hfd_y %>%
      filter(year>1900)%>%
      gather(key="Measure", value = "Units", artist_hotttnesss:duration)%>%
      ggplot(aes(x=year,y=Units))+
      geom_point()+
      facet_wrap(~Measure, scales = "free")

#Plot the first two graphs with different scale..
```





