---
title: "oct_12"
author: "Arun"
date: "2017/10/12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(singer)
library(tidyverse)
```

```{r}
typeof(`%>%`)
class(`%>%`)
typeof(1)
class(1)
typeof('1')
class('1')
class("1")
class(3.2)
typeof(3.2)
typeof(TRUE)
class(TRUE)
typeof(lm)
typeof(c)
class(c)
typeof(singer_locations)
class(singer_locations)
my_plot <- singer_locations %>% 
  ggplot(aes(x=year,y=duration))
class(my_plot)
typeof(my_plot)
x <- list(numb=1,colo='red',plot=my_plot)
typeof(x)
class(x)
str(x)
```
# Matrix
my_Cat <- matrix(data,nrow = rows,ncol = cols)
```{r}
my_cat <- matrix(c(1,2,3,4),nrow=2,ncol = 2,byrow=TRUE)
my_cat
my_cat <- matrix(c(1,2,"a","b"),nrow=2,ncol = 2,byrow=FALSE)
my_cat
data("singer_locations")
```

## change one entry of singer locations from one type to different type
```{r}
trychange <- singer_locations 
  trychange[1,8] <- "zim"
View(trychange)
glimpse(trychange)
```

```{r}
mean(singer_locations$duration,na.rm = TRUE)
mean(trychange[-1,]$duration,na.rm = TRUE) #remove first row
```
# factors
library(gapminder)
glimpse(gapminder)
```{r}
install.packages("forcats")
library(forcats)
library(singer)
```
```{r}
# glimpse(singer_locations)
sl <- singer_locations %>% 
  mutate(art_name_factor = as.factor(artist_name))
glimpse(sl)
```
```{r}
sl <- sl %>% 
  mutate(art_name_factor_base = factor(artist_name))
glimpse(sl)
```

```{r}
x <- c("a","c","b")
as.factor(x)
factor(x)#modify location, no!
```
```{r}
sl %>% 
  mutate(top_an = fct_lump(art_name_factor,n=2)) %>% 
  count(top_an) %>% 
  arrange(-n)
```
### homework: plot mean duration by artist with
### and without lumping
... %>% 
summarise(mean_duration = mean(duration)) %>% 
ggplot(aes(x = artist_name,...))+
......

```{r}
sl <- sl %>% 
mutate(city_factor = ifelse(is.na(city),
                            "Missing_information",
                            city),
  city_factor = as_factor(city_factor))
glimpse(sl)
```
```{r}
sl %>% 
  mutate(top_cities = fct_lump(city_factor,n=7)) %>% 
  count(top_cities)
```

forcats::
# use forcats to clean up the city stuff
# reading and writing to file

read_csv()
install.packages("readxl")
readxl
write_csv() #write from memory to file
readlx::read_xlsx
