---
title: "cm016-notes_and_exercises.Rmd"
output: github_document
---

#### Purrr lesson for stat 545

Lets define some vectors of type int,logical, double and character.
```{r}
(v_log <- c(TRUE, FALSE, FALSE, TRUE))
(v_int <- 1:4)
(v_doub <- 1:4 * 1.2)
(v_char <- letters[1:4])
```

## index a vector

Access the elements of vector by indices
```{r}

v_char[c(FALSE, FALSE, TRUE, TRUE)]
v_char[v_log]

v_doub[2:3]
v_char[-4]

```

```{r}

v_int[0]
typeof(v_int[0])
v_doub[100]
typeof(v_doub[100])

```

```{r}
v_log
as.integer(v_log)
v_int
as.numeric(v_int)
v_doub
as.character(v_doub)
as.character(as.numeric(as.integer(v_log)))
```


```{r}
v_doub_copy <- v_doub
str(v_doub_copy)
v_doub_copy[3] <- "uhoh"
str(v_doub_copy)

```


```{r}
(big_plans <- rep(NA_integer_, 4))
str(big_plans)
big_plans[3] <- 5L
```

Note that big_plans is still integer!
Note that omitting L results in coercion of big_plans to double

```{r}
str(big_plans)
big_plans[1] <- 10
str(big_plans)
```

##lists

```{r}

(x<- list(1:3,c("four","five")))
(y<-list(logical=TRUE,integer=4L,double=4*1.2,character="character"))

(z<-list(letters[26:22],transcendental=c(pi,exp(1)),f=function(x)x^2))
```


Challenge, in list y pull out the second and third elements, 
in list z oull out all the transcendental numbers.

```{r}
y[2:3]
z[2:3]
typeof(z["transcendental"])
z$transcendental
typeof(z[["transcendental"]])

y[["double"]] #double type
y["double"]   #type list
```

Consider how to square the integers 1 through n 

```{r}
n <- 5

#First method
numbers<-list(1:n)
lapply(numbers,function(x) x^2)

#Second Method
(1:n)^2

#Third Method
res<-rep(NA_integer_,n)
for(i in seq_len(n)){
    res[i]<-i^2
}

exp(v_doub)

(l_doub<-as.list(v_doub))

library(purrr)

map_dbl(l_doub,exp)


```


The funtions in purrr are of the form **map_**. 

```{r eval=FALSE}
map(x,f,...)
## maps all the elements of x with the function f.
```

```{r}
library(stringr)
fruit
str(fruit)
```

Challenge is to use map function and a string r function to split all the fruits that have two separate character strings.

```{r}
fruit %>%
  map(str_split," ")

fruit %>%
  map_chr(str_to_upper)
```

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

A great use of purrr's `map()` functions is to dig information out of a non-rectangular data structure and create a neat data frame. Where do these awkward objects come from? Often as JSON or XML from an API. JSON and XML are two plain text formats for non-rectangular data, i.e. for scenarios where CSV is not an option. If you are lucky it's JSON, which is less aggravating, and readily converts to a list you can work with in R.

